---
title: "Zubrod quick analysis"
author: "Riley M. Anderson"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
graphics: yes
output:
  github_document:
    toc: yes
    toc_depth: 5
    pandoc_args: --webtex
  html_document:
    keep_md: yes
    theme: readable
    mathjax: default
  html_notebook:
    code_folding: hide
    theme: readable
    mathjax: default
  pdf_document:
    toc: yes
header-includes:
  \usepackage{float}
  \floatplacement{figure}{H}
editor_options:
  chunk_output_type: console
---

```{r setup, include = F}
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
# @@@@@ Knitr Options
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@

# Set root directory to the project directory
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())


# Set default knitr options: 
# Suppress warnings and messages, cache chunks, 
#  set default figure size to 6x8 at 300 dpi, and save a png and pdf
knitr::opts_chunk$set(warning = F, message = F, collapse = T, cache = T,
    fig.height = 6, fig.width = 8, dpi = 300, # 6x8" @ 300dpi:1800x2400=4.3MP
    dev = 'png', dev.args = list(pdf = list(onefile = F)))

```



## Overview

What is this analysis about?

### Summary of Results
* 

```{r Main_Code, include = F, cache = F}

# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
# @@@@@ Setup - This code is run, but output is hidden
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@

# Load Packages
library(tidyverse) # Needed for data wrangling: dplyr, tidyr, ggplot2
library(cowplot) # Needed for publication-quality ggplots
library(car)

# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
# @@@@@ Data Preparation
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@

# Import datasets
d <- read.csv("Data/Zubrod_data.csv")

walla_ndvi <- read.csv("Data/NDVI_W_all.csv")

walla_ndre <- read.csv("Data/NDRE_W_all.csv")

s_ndre <- read.csv("Data/S_NDRE_all.csv")

```


```{r Data_Wrangling, echo = F, comment = ""}

d <- d %>% 
  mutate(Details = factor(Details))

d1 <- d %>% 
  pivot_longer(cols = c(NDVI_TAMU, NDVI_WSU),
               names_to = "uni",
               values_to = "NDVI")

walla_ndre <- walla_ndre %>% 
  mutate(Details = factor(Details))

walla_ndvi <- walla_ndvi %>% 
  mutate(Details = factor(Details))

s_ndre <- s_ndre %>% 
  mutate(Details = factor(Details))




```

## Correlation between TAMU & WSU NDVI platforms
```{r Graph_name, echo = F}

hard_SP <- d %>% 
  filter(Details == "HiRain_Hard_SP")


sww_SP <- d %>% 
  filter(Details == "HiRain_SWW_SP")


no_spray <- d %>% 
  filter(Details == "Metribuzin_Trail_NoSpray")


spray <- d %>% 
  filter(Details == "Metribuzin_Trial_Spray")


ndvi_cors <- data.frame(c(round(cor(hard_SP$NDVI_TAMU,
                              hard_SP$NDVI_WSU), 2),
             round(cor(sww_SP$NDVI_TAMU,
                 sww_SP$NDVI_WSU), 2),
             round(cor(no_spray$NDVI_TAMU,
                       no_spray$NDVI_WSU), 2),
             round(cor(spray$NDVI_TAMU,
                       spray$NDVI_WSU), 2)),
           levels(d$Details)) %>%
  mutate(levels.d.Details. = factor(levels.d.Details.))

colnames(ndvi_cors) <- c("cors", "Details")

ndvi_cors <- ndvi_cors %>% 
  mutate(cors = paste0("r = ", cors, sep = " "))


p1 <- d %>% filter(Details == "HiRain_Hard_SP") %>% 
  ggplot(aes(x = NDVI_TAMU, NDVI_WSU)) +
  geom_point(shape = 21) +
  geom_smooth(method = lm,
              formula = y ~ x, se = F) +
  geom_label(data = filter(ndvi_cors, 
                           Details == "HiRain_Hard_SP"),
             aes(x = 0.96, y = 0.4, label = cors)) +
  theme_bw(base_size = 16)


p2 <- d %>% filter(Details == "HiRain_SWW_SP") %>% 
  ggplot(aes(x = NDVI_TAMU, NDVI_WSU)) +
  geom_point(shape = 21) +
  geom_smooth(method = lm,
              formula = y ~ x, se = F) +
  geom_label(data = filter(ndvi_cors, 
                           Details == "HiRain_SWW_SP"),
             aes(x = 0.96, y = 0.4, label = cors)) +
  theme_bw(base_size = 16)


p3 <- d %>% filter(Details == "Metribuzin_Trail_NoSpray") %>% 
  ggplot(aes(x = NDVI_TAMU, NDVI_WSU)) +
  geom_point(shape = 21) +
  geom_smooth(method = lm,
              formula = y ~ x, se = F) +
  geom_label(data = filter(ndvi_cors, 
                           Details == "Metribuzin_Trail_NoSpray"),
             aes(x = 0.972, y = 0.65, label = cors)) +
  theme_bw(base_size = 16)


p4 <- d %>% filter(Details == "Metribuzin_Trial_Spray") %>% 
  ggplot(aes(x = NDVI_TAMU, NDVI_WSU)) +
  geom_point(shape = 21) +
  geom_smooth(method = lm,
              formula = y ~ x, se = F) +
  geom_label(data = filter(ndvi_cors, 
                           Details == "Metribuzin_Trial_Spray"),
             aes(x = 0.963, y = 0.62, label = cors)) +
  theme_bw(base_size = 16)

plot_grid(p1, p2, p3, p4,
          labels = c("A", "B", "C", "D"),
          nrow = 2)

```

* **A)** = HiRain_Hard_SP

* **B)** = HiRain_SWW_SP

* **C)** = Metribuzin_Trail_NoSpray

* **D)** = Metribuzin_Trial_Spray


## Checking the interaction (slopes) on NDVI and Yield for different platforms
```{r interactions, echo = F}

d1 %>% 
  ggplot(aes(x = Yield, y = NDVI)) +
  geom_point(shape = 21,
             aes(color = uni)) +
  geom_smooth(method = lm,
              formula = y ~ x,
              aes(color = uni, fill = uni),
              alpha = 0.3, show.legend = F) +
  facet_wrap(~Details) +
  theme_bw(base_size = 16) +
  theme(strip.background = element_blank(),
        legend.title = element_blank())


```


## Models and likelihood ratio test
```{r models, echo = F}

mod1 <- lm(Yield ~ NDVI_WSU * NDVI_TAMU,
           data = d)

summary(mod1)



Anova(mod1, type = "II",
      test.statistic = "LR")

```

* Texas A&M NDVI is a much tighter predictor of Yield.


# NDRE


## Correlation between TAMU & WSU NDRE platforms
```{r NDRE_SP, echo = F}

cor_label_fun <- function(data, treatment){
data %>% filter(Details == treatment) %>% 
  select(starts_with("N")) %>% cor() %>% 
  data.frame() %>% remove_rownames() %>% 
  select(1) %>% slice(2)
}

ndre_cors <- levels(s_ndre$Details) %>% 
  map(~ cor_label_fun(s_ndre, treatment = .x))


ndre_cors <- bind_cols(bind_rows(ndre_cors),
          data.frame(levels(s_ndre$Details)) %>% 
            rename(Details = levels.s_ndre.Details.)) %>% 
  rename(cor_label = NDRE_TAMU) %>% 
  mutate(cor_label = round(cor_label, 3),
         cor_label = paste("r = ", cor_label, sep = ""))

s_ndre %>% 
  ggplot(aes(x = NDRE_TAMU, y = NDRE_WSU)) +
  geom_point() +
  geom_smooth(method = 'lm') +
  geom_label(data = ndre_cors,
            aes(x = 0.25, y = 0.3, label = cor_label)) +
  facet_wrap(~Details) +
  theme_bw(base_size = 16) +
  theme(strip.background = element_blank())

```


## Checking the interaction (slopes) on NDRE and Yield for different platforms
```{r interactions_NDRE, echo = F}

s_ndre %>% 
  pivot_longer(cols = c(NDRE_TAMU, NDRE_WSU),
               values_to = "NDRE",
               names_to = "uni") %>% 
  ggplot(aes(x = Yield, y = NDRE)) +
  geom_point(shape = 21,
             aes(color = uni)) +
  geom_smooth(method = lm,
              formula = y ~ x,
              aes(color = uni, fill = uni),
              alpha = 0.3, show.legend = F) +
  facet_wrap(~Details) +
  theme_bw(base_size = 16) +
  theme(strip.background = element_blank(),
        legend.title = element_blank())


```


## Models and likelihood ratio test (NDRE)
```{r models_NDRE, echo = F}

mod2 <- lm(Yield ~ NDRE_WSU + NDRE_TAMU,
           data = s_ndre)

summary(mod2)

library(car)

Anova(mod2, type = "II",
      test.statistic = "LR")

```

* Texas A&M NDRE is a slightly better predictor of Yield. Both are very good.

# Walla Walla

```{r walla_NDRE_cor, echo = F}


walla_ndre_cors <- levels(walla_ndre$Details) %>% 
  map(~ cor_label_fun(walla_ndre, treatment = .x))


walla_ndre_cors <- bind_cols(bind_rows(walla_ndre_cors),
          data.frame(levels(walla_ndre$Details)) %>% 
            rename(Details = levels.walla_ndre.Details.)) %>% 
  rename(cor_label = NDRE_TAMU) %>% 
  mutate(cor_label = round(cor_label, 3),
         cor_label = paste("r = ", cor_label, sep = ""))

walla_ndre %>% 
  ggplot(aes(x = NDRE_TAMU, y = NDRE_WSU)) +
  geom_point() +
  geom_smooth(method = 'lm') +
  geom_label(data = walla_ndre_cors,
            aes(x = 0.15, y = 0.2, label = cor_label)) +
  facet_wrap(~Details) +
  theme_bw(base_size = 16) +
  theme(strip.background = element_blank())

```

```{r walla_NDVI_cor, echo = F}

walla_ndvi_cors <- levels(walla_ndvi$Details) %>% 
  map(~ cor_label_fun(walla_ndvi, treatment = .x))


walla_ndvi_cors <- bind_cols(bind_rows(walla_ndvi_cors),
          data.frame(levels(walla_ndvi$Details)) %>% 
            rename(Details = levels.walla_ndvi.Details.)) %>% 
  rename(cor_label = NDVI_TAMU) %>% 
  mutate(cor_label = round(cor_label, 3),
         cor_label = paste("r = ", cor_label, sep = ""))

walla_ndvi %>% 
  ggplot(aes(x = NDVI_TAMU, y = NDVI_WSU)) +
  geom_point() +
  geom_smooth(method = 'lm') +
  geom_label(data = walla_ndvi_cors,
            aes(x = 0.93, y = 0.3, label = cor_label)) +
  facet_wrap(~Details) +
  theme_bw(base_size = 16) +
  theme(strip.background = element_blank())

```


## Session Information

```{r Session_Info, echo = F, comment = ""}

# Add session information to help with reproduceability
sessionInfo()


```


