---
title: "Zubrod quick analysis"
author: "Riley M. Anderson"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
graphics: yes
output:
  github_document:
    toc: yes
    toc_depth: 5
    pandoc_args: --webtex
  html_document:
    keep_md: yes
    theme: readable
    mathjax: default
  html_notebook:
    code_folding: hide
    theme: readable
    mathjax: default
  pdf_document:
    toc: yes
header-includes:
  \usepackage{float}
  \floatplacement{figure}{H}
editor_options:
  chunk_output_type: console
---

```{r setup, include = F}
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
# @@@@@ Knitr Options
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@

# Set root directory to the project directory
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())


# Set default knitr options: 
# Suppress warnings and messages, cache chunks, 
#  set default figure size to 6x8 at 300 dpi, and save a png and pdf
knitr::opts_chunk$set(warning = F, message = F, collapse = T, cache = T,
    fig.height = 6, fig.width = 8, dpi = 300, # 6x8" @ 300dpi:1800x2400=4.3MP
    dev = 'png', dev.args = list(pdf = list(onefile = F)))

```



## Overview

What is this analysis about?

### Summary of Results
* 

```{r Main_Code, include = F, cache = F}

# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
# @@@@@ Setup - This code is run, but output is hidden
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@

# Load Packages
library(tidyverse) # Needed for data wrangling: dplyr, tidyr, ggplot2
library(cowplot) # Needed for publication-quality ggplots


# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
# @@@@@ Data Preparation
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@

# Import datasets
d <- read.csv("Data/Zubrod_data.csv")



```


```{r Data_Wrangling, echo = F, comment = ""}

d <- d %>% 
  mutate(Details = factor(Details))

d1 <- d %>% 
  pivot_longer(cols = c(NDVI_TAMU, NDVI_WSU),
               names_to = "uni",
               values_to = "NDVI")

```

## Correlation between TAMU & WSU NDVI platforms
```{r Graph_name, echo = F}

hard_SP <- d %>% 
  filter(Details == "HiRain_Hard_SP")


sww_SP <- d %>% 
  filter(Details == "HiRain_SWW_SP")


no_spray <- d %>% 
  filter(Details == "Metribuzin_Trail_NoSpray")


spray <- d %>% 
  filter(Details == "Metribuzin_Trial_Spray")


ndvi_cors <- data.frame(c(round(cor(hard_SP$NDVI_TAMU,
                              hard_SP$NDVI_WSU), 2),
             round(cor(sww_SP$NDVI_TAMU,
                 sww_SP$NDVI_WSU), 2),
             round(cor(no_spray$NDVI_TAMU,
                       no_spray$NDVI_WSU), 2),
             round(cor(spray$NDVI_TAMU,
                       spray$NDVI_WSU), 2)),
           levels(d$Details)) %>%
  mutate(levels.d.Details. = factor(levels.d.Details.))

colnames(ndvi_cors) <- c("cors", "Details")

ndvi_cors <- ndvi_cors %>% 
  mutate(cors = paste0("r = ", cors, sep = " "))


p1 <- d %>% filter(Details == "HiRain_Hard_SP") %>% 
  ggplot(aes(x = NDVI_TAMU, NDVI_WSU)) +
  geom_point(shape = 21) +
  geom_smooth(method = lm,
              formula = y ~ x, se = F) +
  geom_label(data = filter(ndvi_cors, 
                           Details == "HiRain_Hard_SP"),
             aes(x = 0.96, y = 0.4, label = cors)) +
  theme_bw(base_size = 16)


p2 <- d %>% filter(Details == "HiRain_SWW_SP") %>% 
  ggplot(aes(x = NDVI_TAMU, NDVI_WSU)) +
  geom_point(shape = 21) +
  geom_smooth(method = lm,
              formula = y ~ x, se = F) +
  geom_label(data = filter(ndvi_cors, 
                           Details == "HiRain_SWW_SP"),
             aes(x = 0.96, y = 0.4, label = cors)) +
  theme_bw(base_size = 16)


p3 <- d %>% filter(Details == "Metribuzin_Trail_NoSpray") %>% 
  ggplot(aes(x = NDVI_TAMU, NDVI_WSU)) +
  geom_point(shape = 21) +
  geom_smooth(method = lm,
              formula = y ~ x, se = F) +
  geom_label(data = filter(ndvi_cors, 
                           Details == "Metribuzin_Trail_NoSpray"),
             aes(x = 0.972, y = 0.65, label = cors)) +
  theme_bw(base_size = 16)


p4 <- d %>% filter(Details == "Metribuzin_Trial_Spray") %>% 
  ggplot(aes(x = NDVI_TAMU, NDVI_WSU)) +
  geom_point(shape = 21) +
  geom_smooth(method = lm,
              formula = y ~ x, se = F) +
  geom_label(data = filter(ndvi_cors, 
                           Details == "Metribuzin_Trial_Spray"),
             aes(x = 0.963, y = 0.62, label = cors)) +
  theme_bw(base_size = 16)

plot_grid(p1, p2, p3, p4,
          labels = c("A", "B", "C", "D"),
          nrow = 2)
levels(d1$Details)
```

* **A)** = HiRain_Hard_SP

* **B)** = HiRain_SWW_SP

* **C)** = Metribuzin_Trail_NoSpray

* **D)** = Metribuzin_Trial_Spray





## Checking the interaction (slopes) on NDVI and Yield for different platforms
```{r interactions, echo = F}

d1 %>% 
  ggplot(aes(x = Yield, y = NDVI)) +
  geom_point(shape = 21,
             aes(color = uni)) +
  geom_smooth(method = lm,
              formula = y ~ x,
              aes(color = uni, fill = uni),
              alpha = 0.3, show.legend = F) +
  facet_wrap(~Details) +
  theme_bw(base_size = 16) +
  theme(strip.background = element_blank(),
        legend.title = element_blank()) +
  coord_flip()


```


## Models and likelihood ratio test
```{r models, echo = F}

mod1 <- lm(Yield ~ NDVI_WSU * NDVI_TAMU,
           data = d)

summary(mod1)

library(car)

Anova(mod1, type = "II",
      test.statistic = "LR")

```

* Texas A&M NDVI is a much tighter predictor of Yield.

## Session Information

```{r Session_Info, echo = F, comment = ""}

# Add session information to help with reproduceability
sessionInfo()


```


